---
title: "Grade analysis"
author: "Emmanuel de MOREL"
format: html
echo : false
---

```{r}
library(here)
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(readr)
library(stringr)
grades <- read_delim("C:/Users/demor/OneDrive/Bureau/Master Dauphine/M1/Courses S1/Data Management and Programming/Lecture24;10;23/grades.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
here::i_am("Grade analysis.Rproj")
```
I compute the minimum, maximum, median and mean grade at the Exam and I include the results as a tabble in the rendered document.
```{r}
#Question 2
stat_exam <- summarise(grades, min_exam = min(Exam,na.rm= TRUE), max_exam = max(Exam,na.rm= TRUE), median_exam = median(Exam, na.rm= TRUE), mean_exam = mean(Exam, na.rm= TRUE))

knitr::kable(stat_exam)
```
I count the number of students who did not take the final exam.
```{r}
#Question 3
exam_absent <- sum(is.na(grades$Exam))
print(exam_absent)
```

I sum the number of "NA" find in the column "Exam", there are 60. Thus, there are 60 students who did not take the final exam


I represent graphically the distribution of grades at the Exam by using a bar chart
```{r}
#Question 4
ggplot(grades,(aes(x=Exam))) + geom_bar(na.rm = TRUE, colour="black") + geom_vline(xintercept = quantile(grades$Exam, .5, na.rm = TRUE),na.rm = TRUE, colour = "red") + labs(title = "Distribution of grades at the Exam", caption = "The red line is the median")
```
I compute the number of students in each Group.
```{r}
#Question 5
students_by_groups <- grades %>% group_by(Group) %>% count() %>% rename("number of students" = n)

knitr::kable(students_by_groups)
```
I plot a graph with the number of students in each groups
```{r}
#Question 6
ggplot(students_by_groups, aes(x=`Group`, y=`number of students`)) + geom_col(fill = "grey50", colour = "black") + theme(axis.text.x=element_text(angle=50, size=8, vjust=0.5)) + labs(title = "Number of students in each group")
```
I plot two different types of graph to represent the distribution of the grades at the Exam conditioned by the group.
```{r}
#Question 7

ggplot(grades, aes(x = Group, y = Exam, fill = Group)) + geom_boxplot(na.rm = TRUE) + theme(axis.text.x=element_text(angle=50, size=8, vjust=0.5)) + labs(title = "Exam conditioned by the group", x = "Group", y = "Grades")

ggplot(grades, aes(x = Group, y = Exam, fill = Group)) + geom_violin(na.rm = TRUE, draw_quantiles = c(0.25, 0.5, 0.75))  + theme(axis.text.x=element_text(angle=50, size=8, vjust=0.5)) + labs(title = "Exam conditioned by the group", x = "Group", y = "Grades")
```
I compute the numbers of students who missed the Exam in each Group
```{r}
#Question 8
absent_group_exam <- grades %>% group_by(`Group`) %>% summarise(count = sum(is.na(Exam))) 

knitr::kable(absent_group_exam)

```
I represent graphically the results obtained in the previous question. 
```{r}
#Question 9
ggplot(absent_group_exam, aes(x=Group, y = count)) + geom_col(fill = "grey50", colour = "black") + theme(axis.text.x=element_text(angle=50, size=8, vjust=0.5)) + labs(title = "Number of students who missed the Exam in each Group", x = "Group", y = "Number of students")
```
```{r}
#Question 10
new_df <- grades %>% group_by(Id, Group) %>% pivot_longer(cols = -c("Id","Group"), names_to = "name")
```
I compute the number of missing grades in total for each student

```{r}
#Question 11
absent_student <- new_df %>% group_by(`Id`) %>% summarise(count = sum(is.na(value))) 

```

I plot the distribution of the number of missing grades per student
```{r}
#Question 12
absent_student_distribution <- absent_student %>% group_by(count) %>% summarise(value = n())

ggplot(absent_student_distribution, aes(x=count,y=value)) + geom_col( fill = "grey50", colour = "black") + labs(title = "Distribution of the number of missing grades per student", x = "Number of student", y = "Number of missing grades")


```
I Compute the number of students who missed the Exam in each Group
```{r}
#Question 13
missing_exam <- new_df %>% group_by(`Group`) %>% filter(str_starts(name,"Exam")) %>% summarise(count = sum(is.na(value))) 
  
knitr::kable(missing_exam)
```
By using the new dataframe I compute the number of missing grades for the online each student
```{r}
#Question 14
online_missing_grades <- new_df %>% group_by(`Id`) %>% filter(str_starts(name,"Online_MCQ_")) %>% summarise(online_miss = sum(is.na(value)))
```

I represent graphically the distribution of the grade at the Exam conditioned by the number of missing grade for the online tests.
```{r}
#Question 15
grades_online <- merge(grades, online_missing_grades, by = "Id")
condition_Exam_online <- grades_online %>% group_by(Exam) %>% summarise(online_miss = n()) %>% filter(!is.na(Exam))

ggplot(condition_Exam_online,(aes(x=`online_miss`, y=`Exam`))) + geom_jitter(aes(colour =online_miss)) + labs(title = "Distribution of the grade at the Exam conditioned by the number of missing grade for the online tests ", x = "Number of missing grade for online tests", y = "Grade at the exam") + scale_colour_viridis_c(option="plasma") + geom_smooth(method=lm, formula = 'y ~ x')

knitr::kable(condition_Exam_online)
```
I  create a table with two columns: Id to identify students and Missed with value TRUE
when the student miss at least one MCQ_xx grade and FALSE when they miss no grade. Then, I plot it in a chart.
```{r}
#Question 16
table_missed_MCQ <- new_df %>% group_by(Id) %>% filter(str_starts(name,"MCQ_")) %>% select(`Id`,`value`) %>% summarise(miss = anyNA(value))

ggplot(table_missed_MCQ, aes(x=miss, fill = miss)) + geom_bar() + labs(title = "Number of students who missed at least on grade corresponding to TRUE and number of students who missed no grade corresponding to FALSE") 
```

I create a table with two columns : Group to identify groups and P_missed with the percentage of students in each group who missed at least on MCQ_xx grade. 
```{r}
#Question 17 
group_table_missed_MCQ <- new_df %>% group_by(`Group`) %>% filter(str_starts(name,"MCQ_")) %>% select(`Group`,`value`)

group_table_missed_MCQ$TF <- is.na(group_table_missed_MCQ$value)
group_table_missed_MCQ <- group_table_missed_MCQ %>% group_by(`Group`) %>% select(`Group`,`TF`) %>% summarise(P_missed = mean((`TF`)*100))

knitr::kable(group_table_missed_MCQ)
```
I represent graphically the average grade at the Exam per group as a function of the percentage of missed MCQ_xx. 
```{r}
#Question 18 
avrg_group <- grades %>% group_by(`Group`) %>% select(`Group`,`Exam`) %>% summarise(average = mean(`Exam`, na.rm = TRUE))

avrg_group <- merge(avrg_group,group_table_missed_MCQ, by = "Group")

ggplot(avrg_group, aes(x=`P_missed`, y = `average`)) + geom_jitter(aes(colour =P_missed)) + scale_colour_viridis_c(option="inferno") + geom_smooth(method=lm, formula = 'y ~ x') + labs(title = "The average grade at the Exam per group as a function of the percentage of missed MCQ_xx ", x = "Percentage of missing grades", y = "Average grade at the exam per group")

knitr::kable(avrg_group)
```

